---
title: "Data extraction"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 

library(plyr)
library(dplyr)
library(tidyverse)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)
no_core <- 5
```

## Loading data aggregated in csv file

This section gathers parameters to be specified beforehand.

```{r data loading, echo=FALSE}
raw_data <- read.csv(file = file.path(dir_data, "Indicators_FR8_SEASON_test_1993_2002_v2.csv"), header = TRUE, sep = ",")
```

## Extracting parameters from csv to be used further

List of indicators, years, temporal dimension (number of indicator values per year)

```{r indicators, echo=FALSE}
indic <- unique(raw_data[,"indicator"])
nindic <- length(indic)
an <- unique(raw_data[,"year_"])
nan <- length(an)
dimT <- unique(raw_data[,"month_"]) 
ndimT <- length(dimT)
ngrids <- length(unique(raw_data[,"cellnum"]))
```
## Extracting coordinates related to each cell
We extract the coordinates of each cell to be used for mapping. To do so we pick a random climat type, year and t dimension, as grid range assessed remains the same no matter what are the values of these parameters.
```{r, echo=FALSE}
# latitudes
vect_lat <- raw_data %>% filter(indicator == "moy_tmax", climattype == "REF", year_ == 2000, month_ == 5) %>% 
  arrange(lat,lon) %>%
  select(lat)
save(vect_lat, file = file.path(dir_data, "extract", "lat.RData"))

# longitudes
vect_lon <- raw_data %>% filter(indicator == "moy_tmax", climattype == "REF", year_ == 2000, month_ == 5) %>% 
  arrange(lat,lon) %>%
  select(lon)
save(vect_lon, file = file.path(dir_data, "extract", "lon.RData"))

```
## Extracting indicator values
For each indicator, values are stored in 3 multi-dimensional arrays: one per climat type (reference, prevision, climatology)
Reference array has 3 dimension: grid+year+t
Prevision/climatology arrays have 4 dimensions: grid+year+run+t
N.B.: 75.78 sec elapsed
```{r, echo=FALSE}
cl <- makeCluster(no_core)
registerDoParallel(cl)
tictoc::tic()
foreach(b=1:10, .packages="tidyverse") %dopar%  { # loop on bootstrap samples
  
  rand_year <- sample(1:nan, nan, replace = TRUE) # generate random year series
  for (ind in 1:2){
  
  # indicator type filtering
    indic_data <- raw_data %>% 
      filter(indicator == indic[ind])
    
      # climat type filtering
    obs_data <- indic_data %>% 
      filter(climattype == "REF") %>% 
      arrange(lat,lon)
    
    prev_data <- indic_data %>% 
      filter(climattype == "PS") %>%
      arrange(lat,lon)
    
    clim_data <- indic_data %>% 
      filter(climattype == "CLIMATO") %>% 
      arrange(lat,lon)
      
      # array setting x*year(*run)*t
    run <- unique(clim_data[,"climatscenario"]) # ensemble members (same for climato and prevision)
    nrun <- length(run) # count of ens members - ignoring 0 set for reference only
  
    array_obs <- array(NA, dim=c(ngrids, nan, ndimT))
    array_prev <- array(NA, dim=c(ngrids, nan, nrun, ndimT))
    array_clim <- array(NA, dim=c(ngrids, nan, nrun, ndimT))
    
    for (j in 1:nan){
      y <- rand_year[j]
      for (t in 1:ndimT){
        array_obs[,j,t] <- as.vector(unlist(obs_data %>% filter(year_ == y+1992, month_ == t+4) %>% select(indicatorvalue)))
        for (r in 1:nrun){
        # indicator value extracting
        array_prev[,j,r,t] <- as.vector(unlist(prev_data %>% filter(year_ == y+1992, month_ == t+4, climatscenario == r) %>% select(indicatorvalue)))
        array_clim[,j,r,t] <- as.vector(unlist(clim_data %>% filter(year_ == y+1992, month_ == t+4, climatscenario == r) %>% select(indicatorvalue)))
        }
      }
    }
    nom_ref <- paste0(indic[ind],b,"_ref.RData")
    nom_prev <- paste0(indic[ind],b,"_prev.RData")
    nom_clim <- paste0(indic[ind],b,"_clim.RData")
    
    save(array_obs, file = file.path(dir_data, "extract", nom_ref))
    save(array_prev, file = file.path(dir_data, "extract", nom_prev))
    save(array_clim, file = file.path(dir_data, "extract", nom_clim))
    }
  }
tictoc::toc()
stopCluster(cl)
```
