---
title: "Exploration"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 

library(s2dverification)
library(stats)
library(s2dverification)
library(ggplot2)
library(CSTools)
library(fanplot)
library(dplyr)
library(ggfan)

```

## Parameters 

```{r }

# variable
ind <- 2

# grid
maille <- 18

# temporal aggregation
temp <- 1:6 #(entre 1 et 6)
ntemp <- length(temp)

# bootstrap and cores
no_core <- 6
nboot <- 100

```

## Retrieving original data set

we have to do a trick to find out the first bootstrapped iteration and the run index whithin this iteration matching the year we are interested in (the random sampling doesn't respect chronology)

```{r }

ps_original <- array(NA, dim=c(ngrids, nan, nrun, ntemp))
ref_original <- array(NA, dim=c(ngrids, nan, ntemp))

 for (year in an){
 y <- which(an==year)

       # bootstrap iteration index of the year selected
    load(file = file.path(dir_data, "extract", "years.RData")) # list of years in each bootstrap iteration
     
    list_match <- lapply(rand_year, function(x) which(year == x)) # list of matchs between list of years randomly generated for the bootstrap and the year we are interested in
     
     y_index <- list_match[[1]] # year index within the bootstrap iteration
     b_index <- 1 # bootstrap iteration index
     for (b in 1:(nboot-1)){ # pick the first iteration and first index matching the year we are looking for
       if (length(list_match[[b]])<1 & length(y_index)<1) {y_index <- list_match[[b+1]]; b_index <- b+1}
       else {y_index <- y_index; b_index <- b_index}
     }
     
  nom_prev <- paste0(indic[ind],b_index,"_prev.RData")
  load(file = file.path(dir_data, "extract", nom_prev))
  ps_original[,y,,] <- array_prev[,y_index[1],,temp]
  
  nom_ref <- paste0(indic[ind],b_index,"_ref.RData")
  load(file = file.path(dir_data, "extract", nom_ref))
  ref_original[,y,] <- array_obs[,y_index[1],temp]
}

```

## Data aggregation
We compute temporal and ensemble aggregation: temporal can be a mean or a sum - ensemble mean always

```{r }

ps_agreg <- apply(ps_original[,,,], c(1,2,3), sum)
ps_gridmean <- apply(ps_agreg, c(2,3), mean)
ps_ensmean <- apply(ps_agreg, c(1,2), mean)
ref_agreg <- apply(ref_original[,,], c(1,2), sum)
ref_gridmean <- apply(ref_agreg, 2, mean)

```

## Nuage de points

Attention sum ou mean selon indicateur!

```{r }


# re shaping data: we put them in a table with 3 columns: type(ref or prevision) - year - value 
df_raw <- data.frame() 

for (y in 1:nan){

  df_raw <- rbind(df_raw, data.frame(type = "prevision", year=an[y], value = ps_gridmean[y,]))
  df_raw <- rbind(df_raw, data.frame(type = "ref", year=an[y], value = ref_gridmean[y]))

}

# plotting with ggplot2
ggplot(df_raw, aes(x=year, y=value,  color=type)) + geom_point()+ #stat = "identity", position = "dodge"
  labs(title = paste0(indic[ind], " spatial means"), x="Year", y= "Value")+
      theme_bw()+
       scale_x_continuous(breaks = scales::pretty_breaks(n = 12))

# value of global difference
df_raw %>% group_by(type) %>% summarise(mean_ps=mean(value))

```

## Plot ensemble mean and spread vs observation

```{r }

# re shaping data: we put them in a table with 3 columns: type(ref or prevision) - year - value 

df_psmean <- data.frame() # table with: type - year - value(ensemble mean)
df_quant <- data.frame() # table with: type - year - value(ensemble quantiles)
df_ref <- data.frame() # table with: type - year - value(ensemble quantiles)

for (y in 1:nan){
  
  df_quant <- rbind(df_quant, data.frame(year=an[y], value = ps_agreg[maille, y, ]))
  df_psmean <- rbind(df_psmean, data.frame(year=an[y], value = ps_ensmean[maille, y]))
  df_ref <- rbind(df_ref, data.frame(year=an[y], value = ref_agreg[maille, y]))
}

# reference terciles
ter1_ref <- as.numeric(quantile(ref_agreg[maille, ], probs = 1/3))
ter3_ref <- as.numeric(quantile(ref_agreg[maille, ], probs = 2/3))

# ps terciles
ter1_ps <- as.numeric(quantile(ps_agreg[maille,,], probs = 1/3))
ter3_ps <- as.numeric(quantile(ps_agreg[maille,,], probs = 2/3))

# plot with ggplot2
p <- ggplot(df_quant, aes(x=year, y=value)) + 
  labs(title = paste0(indic[ind], " MJJASO grid ", maille), x="Year", y= "Value")+
      theme_bw()+
       scale_x_continuous(breaks = scales::pretty_breaks(n = 12))

## with geom_fan extra
p + geom_fan(data=df_quant, intervals=c(1,0.1), show.legend = FALSE) + 
  geom_line(data=df_ref, mapping=aes(x=year,y=value), color="#a1d99b", size=0.8) +
  geom_hline(yintercept=ter1_ref, linetype="dashed", color = "#a1d99b", size=0.2) +
  geom_hline(yintercept=ter3_ref, linetype="dashed", color = "#a1d99b", size=0.2) +
  geom_line(data=df_psmean, mapping=aes(x=year,y=value), color="#f03b20", size=0.8) +
  geom_hline(yintercept=ter1_ps, linetype="dashed", color = "#f03b20", size=0.2) +
  geom_hline(yintercept=ter3_ps, linetype="dashed", color = "#f03b20", size=0.2)

# checking function implementation ♥
#p + geom_interval(data=df_quant, intervals=c(1,0.1), outliers=TRUE)
```



