---
title: "Data extraction"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 

library(plyr)
library(dplyr)
library(tidyverse)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)

```

## Parameters 

```{r }

# bootstrap and cores
no_core <- 6
nboot <- 100

```

## Loading and aggregating data in csv file

```{r data loading, echo=FALSE}

raw_data1 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_1993_1998.csv"), header = TRUE, sep = ",")
raw_data2 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_1999_2004.csv"), header = TRUE, sep = ",")
raw_data3 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_2005_2009.csv"), header = TRUE, sep = ",")
raw_data4 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_2010_2016.csv"), header = TRUE, sep = ",")
raw_data <- rbind(raw_data1,raw_data2,raw_data3,raw_data4)

```

## Automatic parameters extraction

List of variables, years, grids, extracted directly from the data set.

```{r indicators, echo=FALSE}

# variables
indic <- unique(raw_data[,"indicator"])
# number of variables
nindic <- length(indic)

# years
an <- unique(raw_data[,"year_"])
# number of years
nan <- length(an)

# number of grids
ngrids <- length(unique(raw_data[,"cellnum"]))


## Coordinates: 
  # >tricky: we pick a random climat type, year and t dimension, as grid range assessed remains the same no matter what are the values of these parameters

  # longitudes
lon <- raw_data %>% filter(indicator == "moy_tmax", climattype == "REF", year_ == 2000, month_ == 5) %>% 
  arrange(lat,lon) %>%
  select(lon)
lon <- as.numeric(unlist(lon))
save(lon, file = file.path(dir_data, "extract", "lon.RData"))

  # latitudes
lat <- raw_data %>% filter(indicator == "moy_tmax", climattype == "REF", year_ == 2000, month_ == 5) %>% 
  arrange(lat,lon) %>%
  select(lat)
lat <- as.numeric(unlist(lat))
save(lat, file = file.path(dir_data, "extract", "lat.RData"))


```

## Extracting indicator values

For each indicator, values are stored in 3 multi-dimensional arrays: one per climat type (reference, prevision, climatology)
Reference array has 3 dimension: grid+year+time
Prevision/climatology arrays have 4 dimensions: grid+year+run+time

```{r, echo=FALSE}

# generating random year series
# rand_year <- list()
# for (b in 1:nboot){
#    rand_year[[b]] <- sample(1:nan, nan, replace = TRUE) 
#  }
#  save(rand_year, file = file.path(dir_data, "extract", "years.RData"))

# array setting x*year(*run)*t
run <- unique(clim_data[,"climatscenario"]) # ensemble members (same for climato and prevision)
nrun <- length(run) # count of ens members - ignoring 0 set for reference only

tictoc::tic() 

for (ind in 1:nindic){

 # indicator type filtering
    indic_data <- raw_data %>% 
      filter(indicator == indic[ind])
    
 # temporal dimension - specific to each indicator
    dimT <- unique(indic_data[,"period_"]) 
    ndimT <- length(dimT)

 # climat type filtering
    obs_data <- indic_data %>% 
      filter(climattype == "REF") %>% 
      arrange(lat,lon)
    
    prev_data <- indic_data %>% 
      filter(climattype == "PS") %>%
      arrange(lat,lon)
    
    clim_data <- indic_data %>% 
      filter(climattype == "CLIMATO") %>% 
      arrange(lat,lon)

 # extracting data
cl <- makeCluster(no_core)
registerDoParallel(cl)

foreach(b=1:nboot, .packages="tidyverse") %dopar%  { # loop on bootstrap samples
  
  # creating arrays to store data: grids*years(*run)*time
  array_obs <- array(NA, dim=c(ngrids, nan, ndimT))
  array_prev <- array(NA, dim=c(ngrids, nan, nrun, ndimT))
  array_clim <- array(NA, dim=c(ngrids, nan, nrun, ndimT))

    for (j in 1:nan){
      y <- rand_year[[b]][j] # we pick a year from the randomize serie
      
      # at first we filter on year
      obs_int <- obs_data %>% 
      filter(year_ == y+1992) 
      prev_int1 <- prev_data %>% 
      filter(year_ == y+1992) 
      clim_int1 <- clim_data %>% 
      filter(year_ == y+1992) 
      
      # then we filter on time dimension (within a year)
      for (t in 1:ndimT){
        array_obs[,j,t] <- as.vector(unlist(obs_int %>% filter(period_ == t+4) %>% select(indicatorvalue)))
        
        prev_int2 <- prev_int1 %>% 
        filter(month_ == t+4) 
        clim_int2 <- clim_int1 %>% 
        filter(month_ == t+4) 
 
      # finally filtering on runs (prevision and climatology only)
        for (r in 1:nrun){
        array_prev[,j,r,t] <- as.vector(unlist(prev_int2 %>% filter(climatscenario == r) %>% select(indicatorvalue)))
        array_clim[,j,r,t] <- as.vector(unlist(clim_int2 %>% filter(climatscenario == r) %>% select(indicatorvalue)))
        }
      }
    }
  
    nom_ref <- paste0(indic[ind],b,"_ref.RData")
    nom_prev <- paste0(indic[ind],b,"_prev.RData")
    nom_clim <- paste0(indic[ind],b,"_clim.RData")
    
    # saving data
    save(array_obs, file = file.path(dir_data, "extract", nom_ref))
    save(array_prev, file = file.path(dir_data, "extract", nom_prev))
    save(array_clim, file = file.path(dir_data, "extract", nom_clim))
    
} 

stopCluster(cl)

}

tictoc::toc()

```
