---
title: "Data extraction"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 

library(plyr)
library(dplyr)
library(tidyverse)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)

```

## Parameters 

```{r }

# bootstrap and cores
no_core <- 6
nboot <- 100

# variables
indicateurs <- c("drain", "draindef", "dtmax35", "dtmax40", "dtmoy25", "drywav", "heatwav")

# runs
run <- seq(from=1, to=25, by=1)
nrun <- length(run)
```

## Loading data in csv file

```{r data loading, echo=FALSE}

# UERRA

raw_drain <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_d_rain.csv"), header = TRUE, sep = ",")
raw_draindef <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_d_raindef.csv"), header = TRUE, sep = ",")
raw_dtmax35 <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_d_tmax_35.csv"), header = TRUE, sep = ",")
raw_dtmax40 <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_d_tmax_40.csv"), header = TRUE, sep = ",")
raw_dtmoy25 <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_d_tmoy_25.csv"), header = TRUE, sep = ",")
raw_drywav <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_dry_wave.csv"), header = TRUE, sep = ",")
raw_heatwav <- read.csv(file = file.path(dir_data, "P05_SEASON_1993_2016_heat_wave.csv"), header = TRUE, sep = ",")

raws <- list()
raws[[1]] <- raw_drain
raws[[2]] <- raw_draindef
raws[[3]] <- raw_dtmax35
raws[[4]] <- raw_dtmax40
raws[[5]] <- raw_dtmoy25
raws[[6]] <- raw_drywav %>% filter(period_ == "SEASONAL")
raws[[7]] <- raw_heatwav %>% filter(period_ == "SEASONAL")

# SAFRAN

raw_safran1 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_1993_1998.csv"), header = TRUE, sep = ",")
raw_safran2 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_1999_2004.csv"), header = TRUE, sep = ",")
raw_safran3 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_2005_2009.csv"), header = TRUE, sep = ",")
raw_safran4 <- read.csv(file = file.path(dir_data, "Extract_Season_Indicators_FR8_pmt541m_2010_2016.csv"), header = TRUE, sep = ",")

raw_safran1 <- rbind(raw_data1,raw_data2,raw_data3,raw_data4)

raw_safran <- read.csv(file = file.path(dir_data, "toto.csv"), header = TRUE, sep = ",")

  # variables
indic_safran <- unique(raw_data[,"indicator"])
  
```

## Automatic parameters extraction

List of variables, years, grids, extracted directly from the data set.

```{r indicators, echo=FALSE}

# years
an <- unique(raw_drain[,"year_"])
# number of years
nan <- length(an)

# temporal dimension - specific to each indicator
dimT <- unique(raw_drain[,"month_"]) 
ndimT <- length(dimT)

# number of grids
ngrids <- length(unique(raw_drain[,"cellnum"]))

## Coordinates: 
  # >tricky: we pick a random climat type, year and t dimension, as grid range assessed remains the same no matter what are the values of these parameters

  # longitudes
raw_filtered <- distinct(raws[[1]],cellnum, .keep_all= TRUE)
lon <- raw_filtered %>% select(lon)
lon <- as.numeric(unlist(lon))

save(lon, file = file.path(dir_data, "extract", "lon_uerra5.RData"))

  # latitudes
lat <- raw_filtered %>% select(lat)
lat <- as.numeric(unlist(lat))

save(lat, file = file.path(dir_data, "extract", "lat_uerra5.RData"))


```

## Extracting indicator values

For each indicator, values are stored in 3 multi-dimensional arrays: one per climat type (reference, prevision, climatology)
Reference array has 3 dimension: grid+year+time
Prevision/climatology arrays have 4 dimensions: grid+year+run+time

```{r, echo=FALSE}

# generating random year series
# rand_year <- list()
# for (b in 1:nboot){
#    rand_year[[b]] <- sample(1:nan, nan, replace = TRUE) 
#  }
#  save(rand_year, file = file.path(dir_data, "extract", "years.RData"))

load(file = file.path(dir_data, "extract", "years.RData")) # list of years in each bootstrap iteration

tictoc::tic() 

for (d in 6:7) {
  
  data <- raws[[d]]
  select_indic <- indicateurs[d]
  
 # climat type filtering
    obs_data <- data %>% 
      filter(climattype == "REF") 
    
    prev_data <- data %>% 
      filter(climattype == "PS") 
    
    clim_data <- data %>% 
      filter(climattype == "CLIMATO") 

 # extracting data
cl <- makeCluster(no_core)
registerDoParallel(cl)

foreach(b=1:nboot, .packages="tidyverse") %dopar%  { # loop on bootstrap samples
  
  array_obs <- array(NA, dim=c(ngrids, nan)) 
  array_prev <- array(NA, dim=c(ngrids, nan, nrun))
  array_clim <- array(NA, dim=c(ngrids, nan, nrun))


    for (j in 1:nan){
      y <- rand_year[[b]][j] # we pick a year from the randomize serie
      
      # at first we filter on year
      obs_int <- obs_data %>% 
      filter(year_ == y) 
      prev_int1 <- prev_data %>% 
      filter(year_ == y) 
      clim_int1 <- clim_data %>% 
      filter(year_ == y) 
      
                                      ### VARIABLES WITHOUT TIME DIMENSION ###
      
      if (d==6|d==7){

        array_obs[,j] <- as.vector(unlist(obs_int %>% select(indicatorvalue))) 
 
      # finally filtering on runs (prevision and climatology only)
        for (r in 1:nrun){
        array_prev[,j,r] <- as.vector(unlist(prev_int1 %>% filter(climatscenario == r) %>% select(indicatorvalue)))
        array_clim[,j,r] <- as.vector(unlist(clim_int1 %>% filter(climatscenario == r) %>% select(indicatorvalue)))
        }

      }
  
                                      ### VARIABLES WITH TIME DIMENSION ###
    
      else{  # creating arrays to store data: grids*years(*run)*time

      # then we filter on time dimension (within a year)
      for (t in c(1:6)){ #ndimT
        array_obs[,j,t] <- as.vector(unlist(obs_int %>% filter(month_ == t+4) %>% arrange(cellnum) %>% select(indicatorvalue))) #month_ or period_
        
        prev_int2 <- prev_int1 %>% 
        filter(month_ == t+4)  #month_ or period_
        clim_int2 <- clim_int1 %>% 
        filter(month_ == t+4)  #month_ or period_
 
      # finally filtering on runs (prevision and climatology only)
        for (r in 1:nrun){
        array_prev[,j,r,t] <- as.vector(unlist(prev_int2 %>% filter(climatscenario == r) %>% arrange(cellnum) %>% select(indicatorvalue)))
        array_clim[,j,r,t] <- as.vector(unlist(clim_int2 %>% filter(climatscenario == r) %>% arrange(cellnum) %>% select(indicatorvalue)))
        }
      }
      }
      
    }
  
    nom_ref <- paste0(select_indic,b,"_ref_uerra5.RData")
    nom_prev <- paste0(select_indic,b,"_prev_uerra5.RData")
    nom_clim <- paste0(select_indic,b,"_clim_uerra5.RData")
    
    # saving data
    save(array_obs, file = file.path(dir_data, "extract", nom_ref))
    save(array_prev, file = file.path(dir_data, "extract", nom_prev))
    save(array_clim, file = file.path(dir_data, "extract", nom_clim))
}
} 

stopCluster(cl)


tictoc::toc()

```
