---
title: "Mapping deterministic scores"
output: html_document
---

```{r}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(tmaptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(ggmap)
library(mapview)
library(grid)
library(ggpubr)
library(rgeos)
```
## Parameter specifications

Indicator to be displayed
Region of interest

```{r}
moi <- c("May","June","July","August","September","October","November")
ind <- 1

ind_fr <- c("Pluie – evaporation", "Somme des pluies","Nombre de jours de pluie","Nombre de jours T max > 25°C", 
             "Nombre de jours T max > 35°C", "Moyenne T max","Moyenne T min","Moyenne T moy")
ind_eng <- c("Rain – evaporation", "Accumulated rainfall","Number of rainy days","Number of days T max > 25°C", 
             "Number of days T max > 35°C", "T max mean","T min mean","T mean mean")

```
## Loading raster

Specific to indicator and year of prevision

```{r}
load(file = file.path(dir_plot, "season_raster", "det_layname.RData")) # loading stack layer names before writeraster changed them

title <- paste0(indic[ind],"_detsign.tif")
stacky <- stack(file.path(dir_plot, "season_raster", title)) # loading stack file

names(stacky) <- c(layername)# re setting original layer names
```
## Creating maps displaying prevision and skill shapefiles through tmap package

We create one shapefile per month from each raster layer extraction

```{r}

## CREATING SHAPEFILE TO BE PLOTTED BY EXTRACTING RASTER LAYER + FACET DISPLAYING 
tmap_mode('plot')
shp_sign <- list()
shp_score <- list()
maprev <- list()
grid.newpage()
page.layout <- grid.layout(nrow = 3, ncol = 3)
pushViewport(viewport(layout = page.layout))


for (m in 1:ndimT){
 
  ### we build the shapefile of most likely tercile 
  sp_score <- rasterToPolygons(stacky[[2+3*(m-1)]]) 
  names(sp_score) <- "Anomaly.Correlation.Coefficient"
  shp_score[[m]] <- st_as_sf(sp_score)

  ### we build the shapefile of most likely tercile 
  sp_sign <- rasterToPolygons(stacky[[3+3*(m-1)]])
  names(sp_sign) <- "significance"
  sp_sign$significance[which(sp_sign$significance==0)] <- NA # to help plotting
  shp_sign[[m]] <- st_as_sf(sp_sign)

  ### mapping
  titre <- paste0(ind_eng[ind]," ","score on"," ", moi[m])
  
  maprev [[m]]<- qtm(shp_score[[m]], fill = "Anomaly.Correlation.Coefficient", fill.style="cont", fill.breaks=c(-1, -0.6, -0.2, 0.2, 0.6, 1),  attr.outside = TRUE, borders = NULL, fill.palette = "RdYlGn")+ 
   tm_shape(shp_sign[[m]])+
   tm_symbols(size ="significance", col = "yellow", scale = 0.1)+
 #tm_grid(y=c(43.487, 43.787), x=c(4,03,4.5,5),  labels.inside.frame = TRUE, alpha = 0, labels.rot = c(0,90))+
 #tm_scale_bar()+
     tm_layout(title = titre, title.position = c("left","bottom"), title.size = 0.5, legend.show = FALSE)

   if (m<4){
  print(maprev[[m]], vp=viewport(layout.pos.row = 1, layout.pos.col = m))
  }
  else {
  print(maprev[[m]], vp=viewport(layout.pos.row = 2, layout.pos.col = m-3))
  }

}

com_legend <- qtm(shp_score[[m]], fill = "Anomaly.Correlation.Coefficient", fill.style="cont", fill.breaks=c(-1, -0.6, -0.2, 0.2, 0.6, 1),  attr.outside = TRUE, borders = NULL, fill.palette = "RdYlGn")+ 
     tm_layout(legend.only = TRUE)

print(com_legend, vp=viewport(layout.pos.row = 3, layout.pos.col = 2))

### trial: adding background map
# tm_shape(ras_prev_complete$tercile)+
#   tm_raster()

```
## Creating maps displaying prevision and skill shapefiles through ggplot package

Same process as above
ISSUE: centroids ain't central!!!!!!

```{r}
mappy <- list()
titre <- paste0(ind_eng[ind]," ACC score")
grid.newpage()
page.layout <- grid.layout(nrow = 2, ncol = 3)
pushViewport(viewport(layout = page.layout))

### BACKGROUND LOADED FROM GOOGLE
# key = "AIzaSyCD2-pP0yfM8aC8sjCB4g--CaCcExP6NhU"; "AIzaSyB24WUzCzX1lErLgsVLtio1c7QxLfw1_SA"
# register_google(key = "AIzaSyB24WUzCzX1lErLgsVLtio1c7QxLfw1_SA")
# back_map <- get_map(location = c(1.2, 41, 10, 46), maptype = "satellite", source = "google") 

### CREATING SHAPEFILES SPECIFIC TO EACH MONTHS - 1 FOR SCORE 1 FOR VALUE SIGNIFICANCE
for (m in 1:ndimT){
  
  # shapefile of score values
  sp_score <- rasterToPolygons(stacky[[2+3*(m-1)]]) 
  names(sp_score) <- "score"
  shp_score[[m]] <- st_as_sf(sp_score)

  # shapefile of score value significance (wilcoxon test outcome)
  sp_sign <- rasterToPoints(stacky[[3+3*(m-1)]], spatial = TRUE)
  names(sp_sign) <- "significance"
  sp_sign$significance[which(sp_sign$significance==0)] <- NA # to help plotting
  # sp_test <- as.data.frame(sp_sign)
  sf_test <- st_as_sf(sp_sign)
  sf_nrm <- remove_missing(sf_test)
  
  sp_si <- rasterToPolygons(stacky[[3+3*(m-1)]])
  sp_pt2 <- st_as_sf(sp_si)
  sp_pt <- st_centroid(sp_pt2,byid=TRUE)
  
### OVERLAYING SHAPEFILE ON GOOGLE BACKGROUND MAP
mappy[[m]] <- ggmap(back_map) + 
  geom_sf(data = shp_score[[m]], aes(fill = score), inherit.aes = FALSE)+
  scale_fill_gradient(low = "orange", high = "green")+
  geom_sf(data = sf_nrm, aes(colour = significance), inherit.aes = FALSE, size = 0.02, show.legend = FALSE)+
  scale_colour_gradient(low = "blue", high = "blue")
  

ggmap(back_map) + 
  geom_sf(data = shp_score[[m]], aes(fill = score), inherit.aes = FALSE)+
  scale_fill_gradient(low = "orange", high = "green")+
  geom_sf(data = sp_pt, aes(colour = significance.6), inherit.aes = FALSE, size = 0.02, show.legend = FALSE)+
  scale_colour_gradient(low = "blue", high = "blue")

#   if (m<4){
#   print(mappy[[m]], vp=viewport(layout.pos.row = 1, layout.pos.col = m))
#   }
#   else {
#   print(mappy[[m]], vp=viewport(layout.pos.row = 2, layout.pos.col = m-3))
#   }
# 
}

m <- 2 # to be specified
map_multiT <- ggarrange(mappy[[1]], mappy[[2]], mappy[[3]], mappy[[4]], mappy[[5]], mappy[[6]], 
                       common.legend = TRUE, labels = moi) + annotate_figure(map_comp, fig.lab = titre) 
map_uniT <- mappy[[m]]

```
