---
title: "Mapping probabilistic forecast"
output: html_document
---

```{r setup, include=FALSE}

dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 

library(maps)
library(nnet)
library(ggplot2)
library(latticeExtra)
library(sp)
library(rgdal)
library(sf)
library(ggmap)
library(maps)
library(ggplot2)
library(latticeExtra)
library(sp)
library(rgdal)
library(sf)
library(ggmap)
library(mapview)
library(ggnewscale)

```

## Parameters 

```{r }

# chosen variable
indicateurs <- c("drain", "draindef", "dtmax35", "dtmax40", "dtmoy25", "drywav", "heatwav") 
indicateur <- indicateurs[5]

# year
select_year <- 2003 # 2011 for water; 2003 for temperature

# chosen quantile
kantile <- "quint" # ter or quint
extremes <- c("first", "last")

# color palette for quantile probability
 palette_lowquant <- c("#9ecae1","#2b8cbe","#08306b")
 palette_highquant<-  c("#fdd0a2","#f16913","#a50f15")
white_midquant <- c("white")

if (kantile=="quint"){
  probthres = 0.35; lastquant = 5
} else {probthres = 0.45; lastquant = 3}

# score value interval
prob_limits <- c(probthres, 0.9)

# trick to get automatically number of grids 
nom_ref <- paste0(indicateur,1,"_ref_uerra5.RData")
load(file = file.path(dir_data, "extract", nom_ref))
ngrids <- dim(array_obs)[1]

```

## TRICK needed TO FIND BACK REAL YEAR

Bootstrapping mixed up years, we need to find "real years" back with a short trick

```{r }

    # bootstrap iteration index of the year selected
load(file = file.path(dir_data, "extract", "years.RData")) # list of years in each bootstrap iteration
     
list_match <- lapply(rand_year, function(x) which(select_year == x)) # list of matchs between list of years randomly generated for the bootstrap and the year we are interested in
     
y_index <- list_match[[1]] # year index within the bootstrap iteration
b_index <- 1 # bootstrap iteration index

for (b in 1:(nboot-1)){ # pick the first iteration and first index matching the year we are looking for
  if (length(list_match[[b]])<1 & length(y_index)<1) {y_index <- list_match[[b+1]]; b_index <- b+1}
  else {y_index <- y_index; b_index <- b_index}
}

```

## Mapping probabilistic previsions through a shapefile

We transform the array of quintile previsions into a shapefile containing gridded values.
In coloured are grids with extreme quintile previsions above 45% threshold. Grids are in white when they do not comply with this condition.
Blue palette is for the 1st quintile. The darker blue is the higher is ensemble probability on this quintile.
Red palette is for the 1st quintile. The darker red is the higher is ensemble probability on this quintile.

```{r }

### BUIDLING SHAPEFILE OF MEAN MSESS VALUES AND THEIR SIGNIFICANCE ###

  ## loading dataframe of prevision and grid coordinates

nom_prev <- paste0(indicateur,b_index,"psprob_uerra5",kantile, ".RData")
load(file = file.path(dir_data, "extract", nom_prev))

 
  
  ## we build a matrix gathering all info needed for the shapefile:

    # coordinates

matrix4shp <- matrix(0, nrow = ngrids, ncol = 5)

load(file = file.path(dir_data, "extract", "lon_uerra5.RData"))
load(file = file.path(dir_data, "extract", "lat_uerra5.RData"))

matrix4shp[,4] <- lat
matrix4shp[,5] <- lon

    # most likely quintile evaluation

  for (i in 1:ngrids) {
    proba <- c(prob_ps[i,y_index[1],1],prob_ps[i,y_index[1],lastquant]) # we create a vector of quintile 1 and quintile 5 proba
    if (length(unique(proba))==2){ # we make sure there is no NA
      quantile <- which.is.max(proba) # most likely quintile
    if (proba[quantile] > probthres){ # likely quintile confidence has to exceed 45%
        matrix4shp[i,quantile] <- proba[quantile]
    }
    }
  }
    
    # setting NA when quintile prob too low or when at least one quintile prob is NA

    # 1st quantile
naindex <- which(matrix4shp[,1]==0) 
matrix4shp[naindex,1] <- NA
    # last quantile
naindex <- which(matrix4shp[,2]==0) 
matrix4shp[naindex,2] <- NA
    # both quantiles
matrix4shp[,3] <- NA
naindex <- which(is.na(matrix4shp[,1]) & is.na(matrix4shp[,2])) 
matrix4shp[naindex,3] <- 0

    # building shapefile 
    
    # we load the dataframe previously built and transform it into a raster
df_shp <- data.frame(matrix4shp)
colnames(df_shp) <- c("first_quantile", "last_quantile", "middle", "lat","lon")
coordinates(df_shp) <- ~lon+lat
proj4string(df_shp) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
shp_confprev <- st_as_sf(df_shp)


### MAPPING WITH GGPLOT2 ###

ggmap(back_map) +
  geom_sf(data = shp_confprev, aes(color = last_quantile), size=0.85, shape = 15) +
  scale_color_gradientn(colours=palette_highquant, limits = prob_limits, na.value = "transparent", guide = guide_colorbar(barwidth = 10, barheight = 0.5, nbin = 5, title = "last quantile probability", order = 3))+
new_scale("color")+
  geom_sf(data = shp_confprev, aes(color = first_quantile), size=0.85, shape = 15) + 
  scale_color_gradientn(colours=palette_lowquant, limits = prob_limits, na.value = "transparent", guide = guide_colorbar(barwidth = 10, barheight = 0.5, nbin = 5, title = "1st quantile probability", order = 1)) +
new_scale("color")+
geom_sf(data = shp_confprev, aes(color = middle), size=0.85, shape = 15) +
  scale_color_gradientn(colours=white_midquant, na.value = "transparent", guide = guide_colorbar(barwidth = 1.5, barheight = 0.5, label = FALSE, frame.colour = "black", title = "no outstanding extreme", order = 2))+
theme(legend.direction = "horizontal",
        legend.box = "vertical",   legend.position = "right",
      plot.title = element_text(size = 12, hjust = 0, vjust = 1.5)) + #
  labs(title = paste0(indicateur," ", select_year," MJJASO ",kantile," forecast "))


```
