---
title: "map_prevconf"
output: html_document
---

```{r}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(ggmap)
library(mapview)
library(grid)
library(ggnewscale)

```
## Parameter specifications

Indicator to be displayed
Month
Region of interest

```{r}
select_year <- 2003
moi <- c("May","June","July","August","September","October","November")
ind <- 2

ind_fr <- c("Pluie – evaporation", "Somme des pluies","Nombre de jours de pluie","Nombre de jours T max > 25°C", 
             "Nombre de jours T max > 35°C", "Moyenne T max","Moyenne T min","Moyenne T moy")
ind_eng <- c("Rain – evaporation", "Accumulated rainfall","Number of rainy days","Number of days T max > 25°C", 
             "Number of days T max > 35°C", "T max mean","T min mean","T mean mean")
palette_terc1 <- c("#c7eae5","#abd9e9","#2166ac")
palette_terc3 <- c("#fde0ef","#f4a582","#b2182b")

```
## Loading raster

Specific to indicator and year of prevision

```{r}

title <- paste0(indic[ind],"_confprevseas", select_year,".tif")
stacky_seas <- stack(file.path(dir_plot, "season_raster", title)) # loading stack file

if (ind!=3 & ind!=4 & ind!=5) { 
  title <- paste0(indic[ind],"_confprevmonth", select_year,".tif")
  stacky_mois <- stack(file.path(dir_plot, "season_raster", title)) # loading stack file
}

load(file = file.path(dir_plot, "season_raster", "layname_confprevmonth.RData")) # loading stack layer names before writeraster changed them
names(stacky_mois) <- c(layername)# re setting original layer names

load(file = file.path(dir_plot, "season_raster", "layname_confprevseas.RData")) # loading stack layer names before writeraster changed them
names(stacky_seas) <- c(layername)# re setting original layer names

```
### MONTHLY MAPS ###

Only for continuous indicators
Creating maps displaying prevision and confidence shapefiles
We create one shapefile per month from each raster layer extraction

```{r}

## CREATING SHAPEFILE TO BE PLOTTED BY EXTRACTING RASTER LAYER + FACET DISPLAYING 
tmap_mode('plot')
shp_tercile <- list()
shp_conf <- list()
maprev <- list()
grid.newpage()
page.layout <- grid.layout(nrow = 3, ncol = 3)
pushViewport(viewport(layout = page.layout))


for (m in 1:ndimT){
 
  ### we build the shapefile of most likely tercile 
  sp_tercile <- rasterToPolygons(stacky_mois[[2+3*(m-1)]]) 
  names(sp_tercile) <- "tercile"
  #sp_tercile@data[,1] <- as.character(sp_tercile@data[,1])
  shp_tercile[[m]] <- st_as_sf(sp_tercile)

  ### we build the shapefile of prevision confidence
  sp_conf <- rasterToPolygons(stacky_mois[[3+3*(m-1)]])
  names(sp_conf) <- "confidence"
  sp_conf$confidence[which(sp_conf$confidence==0)] <- NA # to help plotting
  shp_conf[[m]] <- st_as_sf(sp_conf)
   
#    1st tercile = lower tercile; 2nd = middle; 3rd = upper
  
  ### mapping
  titre <- paste0(ind_eng[ind]," ","for"," ", moi[m], " ", select_year)
  maprev [[m]]<- qtm(shp_tercile[[m]], fill = "tercile",
     attr.outside = TRUE,borders = NULL, fill.style="fixed",fill.breaks=c(1,2,3,4),fill.palette = temp_palette, legend.fill.show=FALSE)+ 
 tm_shape(shp_conf[[m]])+
   tm_symbols(size ="confidence", col = "yellow", scale = 0.01)+
 #tm_grid(y=c(43.487, 43.787), x=c(4,03,4.5,5),  labels.inside.frame = TRUE, alpha = 0, labels.rot = c(0,90))+
 #tm_scale_bar()+
 #tm_add_legend(type = "fill", labels = c("3rd tercile","2nd tercile","1st tercile"), col =  c("dodgerblue3","lightgrey","darkslategray2"), alpha = 0.5)+
     tm_layout(title = titre, title.position = c("left","bottom"), title.size = 0.5, legend.show = FALSE)

   if (m<4){
  print(maprev[[m]], vp=viewport(layout.pos.row = 1, layout.pos.col = m))
  }
  else {
  print(maprev[[m]], vp=viewport(layout.pos.row = 2, layout.pos.col = m-3))
  }

}
#fill.style="fixed",fill.breaks=c(1,2,3,4), 
com_legend <- qtm(shp_tercile[[m]], fill = "tercile",
     attr.outside = TRUE,borders = NULL, fill.style="fixed",fill.breaks=c(1,2,3,4),fill.palette = temp_palette)+  
     tm_layout(legend.only = TRUE)

print(com_legend, vp=viewport(layout.pos.row = 3, layout.pos.col = 2))


```
### SEASONAL MAPS ###

Creating maps displaying prevision and confidence shapefiles


```{r}
sp_tercile1 <- rasterToPolygons(stacky_seas[[2]])
names(sp_tercile1) <- "tercile1"
sp_tercile1$tercile1[which(sp_tercile1$tercile1==0)] <- NA # to help plotting
shp_tercile1 <- st_as_sf(sp_tercile1)

sp_tercile3 <- rasterToPolygons(stacky_seas[[3]])
names(sp_tercile3) <- "tercile3"
sp_tercile3$tercile3[which(sp_tercile3$tercile3==0)] <- NA # to help plotting
shp_tercile3 <- st_as_sf(sp_tercile3)
shp_tercile3 <- remove_missing(shp_tercile3)

ggmap(back_map) +
   geom_sf(data = shp_tercile1, aes(fill = tercile1), inherit.aes = FALSE, alpha = 0.8)+
   scale_fill_gradientn(colours=palette_terc1, limits = c(0.45,1))+ #, na.value="lightgrey"
   new_scale("fill") +
   geom_sf(data = shp_tercile3, aes(fill = tercile3), inherit.aes = FALSE, alpha = 0.8)+
   scale_fill_gradientn(colours=palette_terc3, limits = c(0.45,1))+ #, na.value="lightgrey"
   labs(title = paste0(ind_eng[ind]," season prevision for ",select_year))+
   theme(plot.title = element_text(size = 12, hjust = 0, vjust = 1.5))

```
