---
title: "visu_skilledprev"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure"
library(stats)
no_core <- 5
ind <- 2# indicator selecte
point <- 51# grid index to be used for the normality assessment
event <-2
```

## Combining prevision and skills

We save in one array skill scores over all bootstrapped samples, one for higher and one for lower tercile.
In a same vein, we save in one array probabilistic prevision over all bootstrapped samples, one for higher and one for lower tercile.


```{r}
score_ps <- array(NA, dim=c(ngrids, ndimT, event, 10)) 
score_clim <- array(NA, dim=c(ngrids, ndimT, event, 10)) 
prev_prob <- array(NA, dim=c(ngrids, nan, ndimT, event, 10)) 

for (b in 1:10)  { 

  for (e in 1:2){

  nom_prev <- paste0(indic[ind], b,"scoreprob_grid_prev.RData")
  nom_clim <- paste0(indic[ind], b,"scoreprob_grid_clim.RData")
  load(file = file.path(dir_data, "score", nom_prev))
  load(file = file.path(dir_data, "score", nom_clim))
  
  nom_ps <- paste0(indic[ind],b,"_prob_prev.RData")
  load(file = file.path(dir_data, "extract", nom_ps))

  score_ps[,,e,b] <- scoreprob_ps[,,e]
  score_clim[,,e,b] <- scoreprob_clim[,,e]
  
  prev_prob[,,,e,b] <- prob_ps[,,,e]
  
  }
}

```

## Statistical tests

We compute Wilcoxon test on prevision and climatological skill scores to evaluate the differences, at 95% confidence level. Here we consider only the two events Upper Tercile and Lower Tercile.
We save in one array wilcoxon test outcome with both skill and prevision summaries. The dimensions of the arrays are the following:
grids.tdim.3(=prob prevision + score + wilcoxon test).event

```{r pressure, echo=FALSE}

     # visual assessment of normality - computed per grid
par(mfrow=c(1,2))
hist(score_ps[point,],freq=F)
qqnorm(score_ps[point,])
qqline(score_ps[point,]) #bug

    # Wilcoxon test 
    #
wilcox_df <- array(0, dim=c(ngrids, ndimT,3,event)) 

for (i in 1:ngrids)  { 
for (t in 1:ndimT)  { 
  
wht <- wilcox.test(x = score_clim[i,t,1,], y = score_ps[i,t,1,] ,alternative = "less", paired = TRUE, conf.level = 0.95, na.rm = TRUE)
wlt <- wilcox.test(x = score_clim[i,t,2,], y = score_ps[i,t,2,] ,alternative = "less", paired = TRUE, conf.level = 0.95, na.rm = TRUE)

  if (wht$p.value < 0.05) {
    wilcox_df[i,t,3,1] <- 1 
  }
  if (wlt$p.value < 0.05) {
    wilcox_df[i,t,3,2] <- 1 
  }
}
}
  # summarize score over bootstrapped samples
wilcox_df[,,2,1] <- apply(score_ps[,,,1], c(1,2), mean, na.rm = TRUE)
wilcox_df[,,2,2] <- apply(score_ps[,,,2], c(1,2), mean, na.rm = TRUE)

  # summarize prevision over bootstrapped samples and model runs
wilcox_df[,,1,1] <- apply(prev_prob[,,,1,], c(1,3), mean, na.rm = TRUE)
wilcox_df[,,1,2] <- apply(prev_prob[,,,2,], c(1,3), mean, na.rm = TRUE)


nom <- paste0(indic[ind],"_skilledprev.RData")
save(wilcox_df, file = file.path(dir_data, "score", nom))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
