---
title: "visu_skilledprev"
output: html_document
---

```{r setup, include=FALSE}
library(stats)

dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure"

no_core <- 5
event <-2
```

## Combining prevision and skills

We save in one array skill scores over all bootstrapped samples, one for higher and one for lower tercile, and their associated Wilcoxon test outcomes. The test evaluates whether the prevision predicts better than the climatology, at 0.95 confidence level. 

```{r}
for (ind in 6:8){

  score_ps <- array(NA, dim=c(ngrids, ndimT, event, 1000)) 
  score_clim <- array(NA, dim=c(ngrids, ndimT, event, 1000)) 
  prev_prob <- array(NA, dim=c(ngrids, nan, ndimT, event, 1000)) 
  
      # loading scores (to be summarized later)
  
  for (b in 1:1000)  { 
  
    for (e in 1:2){
  
    nom_prev <- paste0(indic[ind], b,"scoreprob_grid_prev.RData")
    nom_clim <- paste0(indic[ind], b,"scoreprob_grid_clim.RData")
    load(file = file.path(dir_data, "score", nom_prev))
    load(file = file.path(dir_data, "score", nom_clim))
    
    score_ps[,,e,b] <- scoreprob_ps[,,e]
    score_clim[,,e,b] <- scoreprob_clim[,,e]
    
    prev_prob[,,,e,b] <- prob_ps[,,,e]
    
    }
  }
      # extracting Wilcoxon test outcomes for each tercile (0 = ps not better than clim, 1 = ps > clim) 
      
  wilcox_df <- array(0, dim=c(ngrids, ndimT,2,event)) 
  
  for (i in 1:ngrids)  { 
  for (t in 1:ndimT)  { 
    
  wht <- wilcox.test(x = score_clim[i,t,1,], y = score_ps[i,t,1,] ,alternative = "less", paired = TRUE, conf.level = 0.95, na.rm = TRUE)
  wlt <- wilcox.test(x = score_clim[i,t,2,], y = score_ps[i,t,2,] ,alternative = "less", paired = TRUE, conf.level = 0.95, na.rm = TRUE)
  
    if (wht$p.value < 0.05) {
      wilcox_df[i,t,2,1] <- 1 
    }

    if (wlt$p.value < 0.05) {
      wilcox_df[i,t,2,2] <- 1 
    }
  }
  }
    # summarizing scores over bootstrapped samples
  
  wilcox_df[,,1,1] <- apply(score_ps[,,1,], c(1,2), mean, na.rm = TRUE)
  wilcox_df[,,1,2] <- apply(score_ps[,,2,], c(1,2), mean, na.rm = TRUE)
  
  nom <- paste0(indic[ind],"_skills.RData")
  save(wilcox_df, file = file.path(dir_data, "score", nom))

}

```

## Statistical tests

We compute Wilcoxon test on prevision and climatological skill scores to evaluate the differences, at 95% confidence level. Here we consider only the two events Upper Tercile and Lower Tercile.
We save in one array wilcoxon test outcome and skills and prevision summaries. The dimensions of the array is the following:
grids.tdim.2(= wilcoxon test + score).event.
We summarize in another array 

```{r pressure, echo=FALSE}

     # visual assessment of normality - computed per grid
# par(mfrow=c(1,2))
# hist(score_ps[point,],freq=F)
# qqnorm(score_ps[point,])
# qqline(score_ps[point,]) #bug

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
