---
title: "Mapping skilled probabilistic prevision"
output: html_document
---

```{r}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(ggmap)

```

## Parameter setting 

```{r}
moi <- c("May","June","July","August","September","October","November")
select_var <- 2
select_t <- 4
```

## Preparing the dataframe containing previsions and associated skills

We create a conversion-to-shapefile ready dataframe containing the most likely tercile and the values of Wilcoxon test. 

```{r}
# loading dataframe of prevision with associated skills and coordinates

nom <- paste0(indic[select_var],"_skilledprev.RData")
load(file = file.path(dir_data, "score", nom))
load(file = file.path(dir_data, "extract", "lon.RData"))
load(file = file.path(dir_data, "extract", "lat.RData"))

# creating a table containing most likely tercile and its associated wilcoxon outcome, with both coordinates (shape ready for shapefile conversion)

matrix4shp <- matrix(1, nrow = ngrids, ncol = 4)

for (i in 1:ngrids) {
  if (wilcox_df[i,mois,1,1]<wilcox_df[i,select_t,1,2]) # i.e. first tercile most likely to happen
  {matrix4shp[i,1] <- 3
   matrix4shp[i,2] <- wilcox_df[i,select_t,3,2] # extracting wilcoxon score associated to the most likely tercile
    }
}
matrix4shp[,3] <- unlist(vect_lat)
matrix4shp[,4] <- unlist(vect_lon)


```


## Converting the dataframe into shapefiles

We create two polygon shapefiles: one containing most likely tercile forecasted; one containing wilcoxon test outcomes. 

```{r}
# we load the dataframe previously built
df_shp <- data.frame(matrix4shp)
colnames(df_shp) <- c("tercile", "wilcoxon","lat","lon")
coordinates(df_shp) <- ~lon+lat
proj4string(df_shp) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
sp_prev <- st_as_sf(df_shp)
ras_prev <- raster(sp_prev)
ext_prev <- extent(ras_prev)
mask.raster <- raster(resolution=c(0.1,0.1), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0", ## !!!!!!!!!!!
                      ext = ext_prev)
ras_prev_complete <- rasterize(sp_prev, mask.raster)

# we build the shapefile of most likely tercile 
sp_tercile <- rasterToPolygons(ras_prev_complete$tercile)
shp_tercile <- st_as_sf(sp_tercile)
plot(shp_tercile)
titre_terc <- paste0(indic[select_var], "_likelytercile_", moi[select_t],".shp")
st_write(shp_tercile, titre_terc, delete_dsn=TRUE)

# we build the shapefile of most likely tercile 
sp_wilcox <- rasterToPolygons(ras_prev_complete$wilcoxon)
shp_wilcox <- st_as_sf(sp_wilcox)
plot(shp_wilcox)
titre_wil <- paste0(indic[select_var], "_wilcox_", moi[select_t],".shp")
st_write(shp_wilcox, titre_wil, delete_dsn=TRUE)
```


