---
title: "Building ROC with significance rasters"
output: html_document
---

```{r}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(ggmap)
library(nnet)

```

## Parameter setting 

```{r}

moi <- c("May","June","July","August","September","October","November")
event <- 2

```
## Building up rasters merging gridded prevision and confidence - indicator and year specific
For each indicator:
  - We create a conversion-to-raster-ready dataframe containing the most likely tercile and the confidence level (0: conf < 0.5; 1: conf > 0.5).
  - We transform the data frame into a raster, specific to each month
  - We stack all rasters in a rasterstack containing all month and save it

```{r}

for (ind in 6:8){
  
    ## loading dataframe of ROC score
  
  # 1=low tercile, 2=high tercile
  score_ps <- array(NA, dim=c(ngrids, ndimT, event, 1000)) 
  score_clim <- array(NA, dim=c(ngrids, ndimT, event, 1000)) 
  
  for (b in 1:1000)  { 
    
    nom_prev <- paste0(indic[ind], b,"scoreprob_grid_prev.RData")
    nom_clim <- paste0(indic[ind], b,"scoreprob_grid_clim.RData")
    
    load(file = file.path(dir_data, "score", nom_prev))
    load(file = file.path(dir_data, "score", nom_clim))

    score_ps[,,1,b] <- scoreprob_ps[,,2] # low tercile
    score_ps[,,2,b] <- scoreprob_ps[,,1] # high tercile
    score_clim[,,1,b] <- scoreprob_clim[,,2] # low tercile
    score_clim[,,2,b] <- scoreprob_clim[,,1] # high tercile
    
  }
   
  load(file = file.path(dir_data, "extract", "lon.RData"))
  load(file = file.path(dir_data, "extract", "lat.RData"))
  
  matrix4shp <- matrix(0, nrow = ngrids, ncol = 6) #col1: low tercile score; col2: low tercile score signifiance; col3: low tercile score; col4: low tercile score signifiance; col5: latitude; col6: longitude
  
  matrix4shp[,5] <- unlist(vect_lat)
  matrix4shp[,6] <- unlist(vect_lon)
  
  ## creating a table containing mean skill and wilcoxon test outcome, with both coordinates (shape ready for shapefile conversion)
  ras_prev_complete <- list()
  
  for (t in 1:ndimT)  { 
    matrix4shp[,2] <- rep(0, ngrids)
    matrix4shp[,4] <- rep(0, ngrids)
    matrix4shp[,1] <- apply(score_ps[,t,1,], 1, mean, na.rm = TRUE) # summarizing skill scores for LT over bootstrap
    matrix4shp[,3] <- apply(score_ps[,t,2,], 1, mean, na.rm = TRUE) # summarizing skill scores for HT over bootstrap

  for (i in 1:ngrids)  { 
    
  wlt <- wilcox.test(x = score_clim[i,t,1,], y = score_ps[i,t,1,] ,alternative = "less", paired = TRUE, conf.level = 0.95)
  wht <- wilcox.test(x = score_clim[i,t,2,], y = score_ps[i,t,2,] ,alternative = "less", paired = TRUE, conf.level = 0.95)

    if (wlt$p.value < 0.05) {
      matrix4shp[i,2] <- 1 
    }
  
    if (wht$p.value < 0.05) {
      matrix4shp[i,4] <- 1 
    }
  }
  
  # we load the dataframe previously built and transform it into a raster
  
  df_shp <- data.frame(matrix4shp)
  colnames(df_shp) <- c("score_lt", "signifi_lt","score_ht", "signifi_ht","lat","lon")
  coordinates(df_shp) <- ~lon+lat
  proj4string(df_shp) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
  shp_prob <- st_as_sf(df_shp)
  ras_prev <- raster(shp_prob)
  ext_prev <- extent(ras_prev)
  mask.raster <- raster(resolution=c(0.1,0.072), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0", ## !!!!!!!!!!!
                          ext = ext_prev)
  ras_prev_complete[[t]] <- rasterize(shp_prob, mask.raster)
  }
  
  # Stacking rasters from all the different months and saving it
  
  stacky <- stack(ras_prev_complete)
  title <- paste0(indic[ind],"_probsign.tif")
  writeRaster(stacky, filename=file.path(dir_plot, "season_raster", title), overwrite = TRUE)
  
}

layername <- names(stacky)
save(layername, file = file.path(dir_plot, "season_raster", "prob_layname.RData"))
```


