---
title: "Building ROC with significance rasters"
output: html_document
---

```{r}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(ggmap)
library(nnet)
nboot <- 500

```

## Parameter setting 

```{r}

moi <- c("May","June","July","August","September","October","November")
event <- 2

```
## SEASONNAL SCORE RASTER
Building up rasters merging gridded prevision and confidence - indicator and year specific
For each indicator:
  - We create a conversion-to-raster-ready dataframe containing the most likely tercile and the confidence level (0: conf < 0.5; 1: conf > 0.5).
  - We transform the data frame into a raster


```{r}

for (ind in 1:8){
    
      score_ps <- array(NA, dim=c(ngrids, event, nboot)) 
  
    for (b in 1:nboot)  { 
      
      nom_prev <- paste0(indic[ind], b,"scoreprobseason_grid_prev.RData")
  
      load(file = file.path(dir_data, "score", nom_prev))
  
      score_ps[,1,b] <- scoreprob_seas_ps[,1] # low tercile
      score_ps[,2,b] <- scoreprob_seas_ps[,2] # high tercile
    
    }
    
    load(file = file.path(dir_data, "extract", "lon.RData"))
    load(file = file.path(dir_data, "extract", "lat.RData"))
    
    matrix4shp <- matrix(0, nrow = ngrids, ncol = 6) #col1: low tercile score; col2: low tercile score signifiance; col3: low tercile score; col4: low tercile score signifiance; col5: latitude; col6: longitude
    
    matrix4shp[,5] <- unlist(vect_lat)
    matrix4shp[,6] <- unlist(vect_lon)
    
    ## creating a table containing mean skill and wilcoxon test outcome, with both coordinates (shape ready for shapefile conversion)
    ras_prev_complete <- list()
    
      matrix4shp[,2] <- rep(0, ngrids)
      matrix4shp[,4] <- rep(0, ngrids)
      matrix4shp[,1] <- apply(score_ps[,1,], 1, mean, na.rm = TRUE) # summarizing skill scores for LT over bootstrap
      matrix4shp[,3] <- apply(score_ps[,2,], 1, mean, na.rm = TRUE) # summarizing skill scores for HT over bootstrap
  
    for (i in 1:ngrids)  { 
      if (length(which(is.na(score_ps[i,1,])))<200 | length(which(is.na(score_ps[i,2,])))<200){ # above that threshold indicator considered not assessed
      wlt <- wilcox.test(score_ps[i,1,], mu = 0.5, alternative = "greater", conf.level = 0.95, na.action = na.omit)
      wht <- wilcox.test(score_ps[i,2,], mu = 0.5, alternative = "greater", conf.level = 0.95, na.action = na.omit)
  
        if (wlt$p.value < 0.05) {
          matrix4shp[i,2] <- 1 
        }
      
        if (wht$p.value < 0.05) {
          matrix4shp[i,4] <- 1 
        }
      }
      else {matrix4shp[i,1:4] <- rep(-1,4)} # setting -1 if indicator not assessed, row dropped when mapping
  }
  
  # we load the dataframe previously built and transform it into a raster
  
  df_shp <- data.frame(matrix4shp)
  colnames(df_shp) <- c("score_lt", "signifi_lt","score_ht", "signifi_ht","lat","lon")
  coordinates(df_shp) <- ~lon+lat
  proj4string(df_shp) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
  shp_prob <- st_as_sf(df_shp)
  ras_prev <- raster(shp_prob)
  ext_prev <- extent(ras_prev)
  mask.raster <- raster(resolution=c(0.1,0.072), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0", ext = ext_prev)
  ras_season <- rasterize(shp_prob, mask.raster)

  title <- paste0(indic[ind],"_seasonprobsign.tif")
  writeRaster(ras_season, filename=file.path(dir_plot, "season_raster", title), overwrite = TRUE)
} 

layername <- names(ras_season)
save(layername, file = file.path(dir_plot, "season_raster", "probseas_layname.RData"))

```
## MONTHLY SCORE RASTER
Building up rasters merging gridded prevision and confidence - indicator and year specific
For each indicator:
  - We create a conversion-to-raster-ready dataframe containing the most likely tercile and the confidence level (0: conf < 0.5; 1: conf > 0.5).
  - We transform the data frame into a raster, specific to each month
  - We stack month raster as multi layered raster (6 layers)

```{r}

for (ind in c(1,2,6,7,8)){
  
score_ps <- array(NA, dim=c(ngrids, ndimT, event, nboot)) 
  for (b in 1:nboot)  { 
    
    nom_prev <- paste0(indic[ind], b,"scoreprobmonth_grid_prev.RData")

    load(file = file.path(dir_data, "score", nom_prev))

    score_ps[,,1,b] <- scoreprob_month_ps[,,1] # low tercile
    score_ps[,,2,b] <- scoreprob_month_ps[,,2] # high tercile
  
  }
   
  load(file = file.path(dir_data, "extract", "lon.RData"))
  load(file = file.path(dir_data, "extract", "lat.RData"))
  
  matrix4shp <- matrix(0, nrow = ngrids, ncol = 6) #col1: low tercile score; col2: low tercile score signifiance; col3: low tercile score; col4: low tercile score signifiance; col5: latitude; col6: longitude
  
  matrix4shp[,5] <- unlist(vect_lat)
  matrix4shp[,6] <- unlist(vect_lon)
  
  ## creating a table containing mean skill and wilcoxon test outcome, with both coordinates (shape ready for shapefile conversion)
  ras_prev_complete <- list()
  
  for (t in 1:ndimT)  { 
    matrix4shp[,2] <- rep(0, ngrids)
    matrix4shp[,4] <- rep(0, ngrids)
    matrix4shp[,1] <- apply(score_ps[,t,1,], 1, mean, na.rm = TRUE) # summarizing skill scores for LT over bootstrap
    matrix4shp[,3] <- apply(score_ps[,t,2,], 1, mean, na.rm = TRUE) # summarizing skill scores for HT over bootstrap

  for (i in 1:ngrids)  { 
    
  wlt <- wilcox.test(score_ps[i,t,1,], mu = 0.5, alternative = "greater", conf.level = 0.95, na.action = na.omit)
  wht <- wilcox.test(score_ps[i,t,2,], mu = 0.5, alternative = "greater", conf.level = 0.95, na.action = na.omit)

    if (wlt$p.value < 0.05) {
      matrix4shp[i,2] <- 1 
    }
  
    if (wht$p.value < 0.05) {
      matrix4shp[i,4] <- 1 
    }
  }
  
  # we load the dataframe previously built and transform it into a raster
  
  df_shp <- data.frame(matrix4shp)
  colnames(df_shp) <- c("score_lt", "signifi_lt","score_ht", "signifi_ht","lat","lon")
  coordinates(df_shp) <- ~lon+lat
  proj4string(df_shp) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
  shp_prob <- st_as_sf(df_shp)
  ras_prev <- raster(shp_prob)
  ext_prev <- extent(ras_prev)
  mask.raster <- raster(resolution=c(0.1,0.072), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0", 
                        ext = ext_prev)
  ras_prev_complete[[t]] <- rasterize(shp_prob, mask.raster)
  }
  
  # Stacking rasters from all the different months and saving it
  
  stacky <- stack(ras_prev_complete)
  title <- paste0(indic[ind],"_monthprobsign.tif")
  writeRaster(stacky, filename=file.path(dir_plot, "season_raster", title), overwrite = TRUE)
  
}

layername <- names(stacky)
save(layername, file = file.path(dir_plot, "season_raster", "probmonth_layname.RData"))
```


