---
title: "Quintile scoring"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure"

library(easyVerification)
library(verification)
library(dplyr)
library(stats)
library(SpecsVerification)
library(s2dverification)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)
library(readr)
library(purrr)

no_core <- 6
nboot <- 500

```

## Loading latitude file

To be used for weighted aggregation.

```{r }
load(file = file.path(dir_data, "extract", "lat.RData"))
lat <- as.vector(vect_lat)

```


## Box-agregated scores

Aggregation computed using latitude weighting

```{r}
tictoc::tic()

for (ind in 2:8){
  list_boot1 <- list()
  list_boot2 <- list()
  list_event1 <- list()
  vect_event2 <- vector()
  
  for (b in 1:nboot){
    nom_prevseas <- paste0(indic[ind],b,"_seasquint_prev.RData")
    nom_refseas <- paste0(indic[ind],b,"_seasquint_obs.RData")
    load(file = file.path(dir_data, "extract", nom_prevseas))
    load(file = file.path(dir_data, "extract", nom_refseas))
    ev <- 0

    for (e in c(1,5)){ #LQ,HQ
      ev <- ev+1
      # if (ind!=3 & ind!=4 & ind!=5) { # monthly
      #   nom_ref <- paste0(indic[ind],b,"_monthquint_obs.RData")
      #   nom_prev <- paste0(indic[ind],b,"_monthquint_prev.RData")
      #   load(file = file.path(dir_data, "extract", nom_ref))
      #   load(file = file.path(dir_data, "extract", nom_prev))
      #   vect_month <- vector()
      #   
      #   for (t in 1: ndimT){
      #      vect_month[t] <- score_boite_prob(monthprob_ps[,,t,], monthbin_ref[,,t,], lat[,1], nb_bin = 5, e)$AUC
      #   }
      # 
      #   vect_month <- vector()
      #   list_event1[[ev]] <- vect_month
      # }
      
      vect_event2[ev] <- score_boite_prob(seasprob_ps, seasbin_ref, lat[1], nb_bin = 5, e)$AUC # seasonal 
    }
    
    # if (ind!=3 & ind!=4 & ind!=5) { # monthly
    # list_boot1[[b]] <- list_event1 # monthtly 
    # }
    
    list_boot2[[b]] <- vect_event2 # seasonal 
    
  }
 
  # if (ind!=3 & ind!=4 & ind!=5) { # monthly
  # nom_month <- paste0(indic[ind],"boxquint_month.RData")
  # save(list_boot1, file = file.path(dir_data, "score", nom_month))
  # }
  
  nom_seas <- paste0(indic[ind],"boxquint_seas.RData")
  save(list_boot2, file = file.path(dir_data, "score", nom_seas))

}

tictoc::toc()

```
## Box-agregated score analysis

Transform lists in a more handy format

```{r}
event <- 2

for (ind in 2:8){
  
   # season
  nom_ps <- paste0(indic[ind],"boxquint_seas.RData")
  load(file = file.path(dir_data, "score", nom_ps))
  
  sum_seas <- apply(array(unlist(list_boot2) , c(event,nboot)), 1, mean, na.rm = T)
  
  nom_seas <- paste0(indic[ind],"avboxquint_seas.csv")
  write_csv(as.data.frame(sum_seas), file.path(dir_data, "score", nom_seas))
  
  # month
  if (ind!=3 & ind!=4 & ind!=5) { # monthly
  nom_ps <- paste0(indic[ind],"boxquint_month.RData")
  load(file = file.path(dir_data, "score", nom_ps))
  
  sum_month <- apply(array(unlist(list_boot1) , c(6,event,nboot)), c(1,2), mean, na.rm = T)
  
  colnames(sum_month) <- c("LQ","HQ")
  nom_month <- paste0(indic[ind],"avboxquint_month.csv")
  write_csv(as.data.frame(sum_month), file.path(dir_data, "score", nom_month))
  
}

}

```
## Box score significance test

Wilcoxon test with H0: AUC non supérieure à 0.5

```{r}
event <- 5
ind <- 2
wlt_month <- vector()
wht_month <- vector()

   # season
  nom_ps <- paste0(indic[ind],"boxquint_seas.RData")
  load(file = file.path(dir_data, "score", nom_ps))
  
  boxboot <- array(unlist(list_boot2) , c(event,nboot))
  
  wlt <- wilcox.test(boxboot[1,], mu = 0.5, alternative = "greater", conf.level = 0.95, na.action = na.omit)$p.value
  wht <- wilcox.test(boxboot[5,], mu = 0.5, alternative = "greater", conf.level = 0.95, na.action = na.omit)$p.value

```
## Gridded scores

Scores computed for each grid separately.
Continuous indicators are assessed monthly while discrete indicators are assessed on whole aggregated season = 6 months (monthly summaries are summed up). 

```{r}
tictoc::tic()
e <- 2

for (ind in 2:8){
  
  cl <- makeCluster(no_core)
  registerDoParallel(cl)

foreach(b=1:nboot, .packages = 'easyVerification') %dopar%  { # loop on bootstrap samples

  nom_ref <- paste0(indic[ind],b,"_ref.RData")
  nom_prev <- paste0(indic[ind],b,"_prev.RData")

  load(file = file.path(dir_data, "extract", nom_ref))
  load(file = file.path(dir_data, "extract", nom_prev))

  # only continuous indicators assessed monthly
    scoreprob_month_ps <- array (NA, dim=c(ngrids,ndimT,e))
    scoreprob_seas_ps <- array (NA, dim=c(ngrids,e))
    
    # monthly
    if (ind!=3 & ind!=4 & ind!=5) { 
       for (t in 1:ndimT){
        scoreprob_month_ps[,t,1] <- veriApply("EnsRoca", fcst=array_prev[,,,t], obs=array_obs[,,t], prob=1/5, parallel = TRUE)$cat1 
        scoreprob_month_ps[,t,2] <- veriApply("EnsRoca", fcst=array_prev[,,,t], obs=array_obs[,,t], prob=4/5, parallel = TRUE)$cat1 
       }
    nom_prevmont <- paste0(indic[ind], b,"scorequintmonth_grid_prev.RData")
    save(scoreprob_month_ps, file = file.path(dir_data, "score", nom_prevmont))
    }
    
    # seasonal
    seas_obs <- apply(array_obs[,,],c(1,2), sum)
    seas_prev <- apply(array_prev[,,,],c(1,2,3), sum)
    
    scoreprob_seas_ps[,1] <- veriApply("EnsRoca", fcst=seas_prev, obs=seas_obs, prob=1/5, parallel = TRUE)$cat1 
    scoreprob_seas_ps[,2] <- veriApply("EnsRoca", fcst=seas_prev, obs=seas_obs, prob=4/5, parallel = TRUE)$cat1 
   
    nom_prevseas <- paste0(indic[ind], b,"scorequintseason_grid_prev.RData")
    save(scoreprob_seas_ps, file = file.path(dir_data, "score", nom_prevseas))

  }

stopCluster(cl)
}

tictoc::toc()



```
