---
title: "Decile detection scoring"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure"

library(easyVerification)
library(verification)
library(dplyr)
library(stats)
library(SpecsVerification)
library(s2dverification)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)
library(readr)
library(purrr)

no_core <- 6
nboot <- 500

```

## Loading latitude file

To be used for weighted aggregation.

```{r }
load(file = file.path(dir_data, "extract", "lat.RData"))
lat <- as.vector(vect_lat)

```


## Box-agregated scores

Aggregation computed using latitude weighting

```{r}
tictoc::tic()

for (ind in 2:8){
  list_boot1 <- list()
  list_boot2 <- list()
  list_event1 <- list()
  vect_event2 <- vector()
  ev <- 0
  for (e in c(1,10)){ #LT,MT,HT
    ev <- ev+1
    for (b in 1:nboot){
    nom_prevseas <- paste0(indic[ind],b,"_seasdecile_prev.RData")
    nom_refseas <- paste0(indic[ind],b,"_seasdecile_obs.RData")
    load(file = file.path(dir_data, "extract", nom_prevseas))
    load(file = file.path(dir_data, "extract", nom_refseas))
    
    if (ind!=3 & ind!=4 & ind!=5) { # monthly
      nom_ref <- paste0(indic[ind],b,"_monthdecile_obs.RData")
      nom_prev <- paste0(indic[ind],b,"_monthdecile_prev.RData")
      load(file = file.path(dir_data, "extract", nom_ref))
      load(file = file.path(dir_data, "extract", nom_prev))
      vect_month <- vector()
      
      for (t in 1: ndimT){
         vect_month[t] <- score_boite_prob(monthprob_ps[,,t,], monthbin_ref[,,t,], lat[,1], nb_bin = 5, e)$AUC
       }

    }

     if (ind!=3 & ind!=4 & ind!=5) { # monthly
       vect_month <- vector()
       
     list_event1[[ev]] <- vect_month
     }

    

   
    vect_event2[ev] <- score_boite_prob(seasprob_ps, seasbin_ref, lat[,1], nb_bin = 5, e)$AUC # seasonal 

   }
  
  if (ind!=3 & ind!=4 & ind!=5) { # monthly
  list_boot1[[b]] <- list_event1 # monthtly 
  }
  
  list_boot2[[b]] <- vect_event2 # seasonal 
  
  }
 
  if (ind!=3 & ind!=4 & ind!=5) { # monthly
  nom_month <- paste0(indic[ind],"boxdecile_month.RData")
  save(list_boot1, file = file.path(dir_data, "score", nom_month))
  }
  
  nom_seas <- paste0(indic[ind],"boxdecile_seas.RData")
  save(list_boot2, file = file.path(dir_data, "score", nom_seas))

}

tictoc::toc()

```
## Box-agregated score analysis

Transform lists in a more handy format

```{r}

for (ind in 2:8){
  
   # season
  nom_ps <- paste0(indic[ind],"boxdecile_seas.RData")
  load(file = file.path(dir_data, "score", nom_ps))
  
  sum_seas <- apply(array(unlist(list_boot2) , c(3,nboot)), 1, mean, na.rm = T)
  
  nom_seas <- paste0(indic[ind],"avboxdecile_seas.csv")
  write_csv(as.data.frame(sum_seas), file.path(dir_data, "score", nom_seas))
  
  # month
  if (ind!=3 & ind!=4 & ind!=5) { # monthly
  nom_ps <- paste0(indic[ind],"boxdecile_month.RData")
  load(file = file.path(dir_data, "score", nom_ps))
  
  sum_month <- apply(array(unlist(list_boot1) , c(6,3,nboot)), c(1,2), mean, na.rm = T)
  
  colnames(sum_month) <- c("LT","MT","HT")
  nom_month <- paste0(indic[ind],"avboxdecile_month.csv")
  write_csv(as.data.frame(sum_month), file.path(dir_data, "score", nom_month))
  
}

}

```


## Gridded scores

Scores computed for each grid separately.
Continuous indicators are assessed monthly while discrete indicators are assessed on whole aggregated season = 6 months (monthly summaries are summed up). 

```{r}
tictoc::tic()
e <- 2

for (ind in 1:8){
  
  cl <- makeCluster(no_core)
  registerDoParallel(cl)

foreach(b=1:nboot, .packages = 'easyVerification') %dopar%  { # loop on bootstrap samples

  nom_ref <- paste0(indic[ind],b,"_ref.RData")
  nom_prev <- paste0(indic[ind],b,"_prev.RData")

  load(file = file.path(dir_data, "extract", nom_ref))
  load(file = file.path(dir_data, "extract", nom_prev))

  # only continuous indicators assessed monthly
    scoreprob_month_ps <- array (NA, dim=c(ngrids,ndimT,e))
    scoreprob_seas_ps <- array (NA, dim=c(ngrids,e))
    
    # monthly
    if (ind!=3 & ind!=4 & ind!=5) { 
       for (t in 1:ndimT){
        scoreprob_month_ps[,t,1] <- veriApply("EnsRoca", fcst=array_prev[,,,t], obs=array_obs[,,t], prob=1/10, parallel = TRUE)$cat1 
        scoreprob_month_ps[,t,2] <- veriApply("EnsRoca", fcst=array_prev[,,,t], obs=array_obs[,,t], prob=9/10, parallel = TRUE)$cat1 
       }
    }
    
    # seasonal
    seas_obs <- apply(array_obs[,,],c(1,2), sum)
    seas_prev <- apply(array_prev[,,,],c(1,2,3), sum)
    
    scoreprob_seas_ps[,1] <- veriApply("EnsRoca", fcst=seas_prev, obs=seas_obs, prob=1/10, parallel = TRUE)$cat1 
    scoreprob_seas_ps[,2] <- veriApply("EnsRoca", fcst=seas_prev, obs=seas_obs, prob=9/10, parallel = TRUE)$cat1 
   
    nom_prevmont <- paste0(indic[ind], b,"scoredecilemonth_grid_prev.RData")
    nom_prevseas <- paste0(indic[ind], b,"scoredecileseason_grid_prev.RData")

    save(scoreprob_month_ps, file = file.path(dir_data, "score", nom_prevmont))
    save(scoreprob_seas_ps, file = file.path(dir_data, "score", nom_prevseas))

  }

stopCluster(cl)
}

tictoc::toc()



```
