---
title: "Ensemble spread visualization"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(ggmap)
```

## Loading files

We load indicator values previously extracted, related to prevision, climatology, or observation. We also load grid coordinate dataframes, required further for mapping.        

```{r file loading}
# parameter specification
ind <- 2 # indicator

# file loading
nom_ref <- paste0(indic[ind],"_ref.RData")
nom_prev <- paste0(indic[ind],"_prev.RData")
nom_clim <- paste0(indic[ind],"_clim.RData")

load(file = file.path(dir_data, "extract", nom_ref))
load(file = file.path(dir_data, "extract", nom_prev))
load(file = file.path(dir_data, "extract", nom_clim))

load(file = file.path(dir_data, "extract", "lon.RData"))
load(file = file.path(dir_data, "extract", "lat.RData"))

```
## Data preparation

We compute ensemble variances of seasonal mean, and average them over the years. To be able to map them afterward, we transform the data frame produced into a raster.

```{r }
# computing variance
clim_values <- apply(array_clim[,,,],c(1,2,3), mean) # seasonal averaging
prev_values <- apply(array_prev[,,,],c(1,2,3), mean) # seasonal averaging

var_prev_y <- apply(prev_values,c(1,2), var)
var_clim_y <- apply(clim_values,c(1,2), var)

var_prev_av <- apply(var_prev_y,c(1), mean)
var_clim_av <- apply(var_clim_y,c(1), mean)

# creating shapefiles of values to be plotted
df_prev <- data.frame(longitude=vect_lon, latitude=vect_lat, indicator=var_prev_av)
df_clim <- data.frame(longitude=vect_lon, latitude=vect_lat, indicator=var_clim_av)

coordinates(df_prev) <- ~lon+lat ### ISSUES COLUMN NAMING !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
coordinates(df_clim) <- ~lon+lat

proj4string(df_prev) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
proj4string(df_clim) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

sp_prev <- st_as_sf(df_prev)
sp_clim <- st_as_sf(df_clim)

plot(sp_prev, nbreaks = 40)
plot(sp_clim, nbreaks = 40)

# transform shp into raster to get data extent 
ras_prev <- raster(sp_prev)
ras_clim <- raster(sp_clim)

ext_prev <- extent(ras_prev)
ext_clim <- extent(ras_clim)

# create background raster 
mask.raster <- raster(resolution=c(0.1,0.07), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0", ## !!!!!!!!!!!
                      ext = ext_prev)

# convert the shapefile to a raster based on background raster
ras_prev_complete <- rasterize(sp_prev, mask.raster)
ras_clim_complete <- rasterize(sp_clim, mask.raster)

plot(ras_prev_complete$indicator)
```
### Mapping ensemble spread

Now that we have computed ensemble variances and transformed the data frame into a raster we will map them using 'tmap' package, and save the maps all together using 'tmap_arrange' function.

```{r }
year <- 3
titre_prev <- paste0(an[year] , " ", indic[ind], " prevision spread ")
titre_clim <- paste0(an[year] , " ", indic[ind], " climato spread ")

rivers <- st_read(dsn=file.path(dir_data, "COURS_D_EAU.shp"))
#proj4string(france_shp) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")


prev_map <- 
  tm_grid(labels.margin.x = -10)+ # increase margin a bit !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
  tm_shape(ras_prev_complete$indicator)+
  tm_raster(title = titre_prev, palette = '-RdBu',
             legend.reverse = TRUE)+
  tm_legend(outside=TRUE, hist.width=2)+
  tm_layout(legend.position = c("left", "bottom"))+
  tm_shape(rivers) +
  tm_sf()
  

clim_map <- 
  tm_grid(labels.margin.x = -10)+ 
  tm_shape(ras_clim_complete$indicator)+
  tm_raster( title = titre_clim, palette = '-RdBu',
             legend.reverse = TRUE)+
  tm_legend(outside=TRUE, hist.width=2)+
  tm_layout(legend.position = c("left", "bottom"))+
  tm_shape(rivers) +
  tm_sf()+

### SAVING MAP    -------------------------------------------------------------------------------------
tiff(paste0(an[year], " seasonal_ens_mean.tiff"), width = 8, height = 5, units = 'in', res = 300, compression = 'none')
tmap_arrange(prev_map, clim_map, asp = 1)
dev.off()

```




