---
title: "Yearly ensemble spread graph"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(s2dverification)

nboot <-500
```


## Parameter setting

We load extracted indicator values, depending on indicator picked (to be specified just below).

```{r file loading}
# parameter specification
ind <- 2 # indicator
```
## Retrieving original data set

we have to do a trick to find out the first bootstrapped iteration and the run index whithin this iteration matching the year we are interested in (the random sampling doesn't respect chronology)

```{r }

ps_original <- array(NA, dim=c(ngrids, nan, nrun, ndimT))
ref_original <- array(NA, dim=c(ngrids, nan, ndimT))

 for (y in 1:nan){

       # bootstrap iteration index of the year selected
    load(file = file.path(dir_data, "extract", "years.RData")) # list of years in each bootstrap iteration
     
    list_match <- lapply(rand_year, function(x) which(y == x)) # list of matchs between list of years randomly generated for the bootstrap and the year we are interested in
     
     y_index <- list_match[[1]] # year index within the bootstrap iteration
     b_index <- 1 # bootstrap iteration index
     for (b in 1:(nboot-1)){ # pick the first iteration and first index matching the year we are looking for
       if (length(list_match[[b]])<1 & length(y_index)<1) {y_index <- list_match[[b+1]]; b_index <- b+1}
       else {y_index <- y_index; b_index <- b_index}
     }
     
  nom_prev <- paste0(indic[ind],b_index,"_prev.RData")
  load(file = file.path(dir_data, "extract", nom_prev))
  ps_original[,y,,] <- array_prev[,y_index[1],,]
  
  nom_ref <- paste0(indic[ind],b_index,"_ref.RData")
  load(file = file.path(dir_data, "extract", nom_ref))
  ref_original[,y,] <- array_obs[,y_index[1],]
}

```
## Spatial standard deviation - monthly


```{r }

### CONTINUOUS INDICATORS ###

  # parameters #
month <- 3
#########

spread_ps <- vector()
spread_ref <- vector()
df_month <- data.frame()

for (y in 1:nan){

  sd_ps <- Spread(ps_original[,y,,month], posdim = c(1,2), narm = TRUE, conf = FALSE)$sd
  sd_ref <- sd(ref_original[,y,month])
  df_month <- rbind(df_month, data.frame(type = "prevision", year=an[y], value = sd_ps))
  df_month <- rbind(df_month, data.frame(type = "ref", year=an[y], value = sd_ref))

}

### buidling up graph   
  ggplot(df_month, aes(factor(year), value)) + geom_point(aes(fill=type, colour =type))+
  labs(title = paste0(indic[ind], " standard deviation lead time ", month), x="Year", y= "Sd")+
    theme_light()
  
# inter <- df_value %>% filter(type=="prevision")
# length(unique(inter[,3]))

  
```
## Spatial standard deviation - season
attention: faire un apply mean pour indicateurs non cumulatifs

```{r }

### CONTINUOUS AND DISCRETE INDICATORS ###
### attention: faire un apply mean pour indicateurs non cumulatifs

spread_ps <- vector()
spread_ref <- vector()
df_seas <- data.frame()

ps_season <- apply(ps_original, c(1,2,3), mean)
ref_season <- apply(ref_original, c(1,2), mean)

for (y in 1:nan){

  sd_ps <- Spread(ps_season[,y,], posdim = c(1,2), narm = TRUE, conf = FALSE)$sd
  sd_ref <- sd(ref_season[,y])
  df_seas <- rbind(df_seas, data.frame(type = "prevision", year=an[y], value = sd_ps))
  df_seas <- rbind(df_seas, data.frame(type = "ref", year=an[y], value = sd_ref))

}

### buidling up graph   
  ggplot(df_seas, aes(factor(year), value)) + geom_point(aes(fill=type, colour =type))+
  labs(title = paste0(indic[ind], " seasonal standard deviation"), x="Year", y= "Sd")+
    theme_light()
  
# inter <- df_value %>% filter(type=="prevision")
# length(unique(inter[,3]))
  
  
```
