---
title: "Yearly ensemble spread graph"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)

```


## Loading files

We load extracted indicator values, depending on indicator picked (to be specified just below).

```{r file loading}
# parameter specification
ind <- 8 # indicator

# file loading
nom_ref <- paste0(indic[ind],"_ref.RData")
nom_prev <- paste0(indic[ind],"_prev.RData")
nom_clim <- paste0(indic[ind],"_clim.RData")
nom_av_clim <- paste0(indic[ind],"_ensmean_clim.RData")
nom_av_prev <- paste0(indic[ind],"_ensmean_prev.RData")

load(file = file.path(dir_data, "extract", nom_ref))
load(file = file.path(dir_data, "extract", nom_prev))
load(file = file.path(dir_data, "extract", nom_clim))
load(file = file.path(dir_data, "extract", nom_av_clim))
load(file = file.path(dir_data, "extract", nom_av_prev))

```
## Ensemble variance 

We compute and plot seasonal yearly ensemble variance for prevision and climatology.

```{r }
### data preparation: computing yearly seasonal ensemble variance for prevision and climatology
df_value <- data.frame()
for (y in 1:nan){
  clim_values <- apply(array_clim[,y,,],c(1,2), mean) # seasonal averaging
  prev_values <- apply(array_prev[,y,,],c(1,2), mean) # seasonal averaging
  
  var_prev <- mean(apply(prev_values,c(1), var))
  var_clim <- mean(apply(clim_values,c(1), var))
  
  df_value <- rbind(df_value, data.frame(type = "prevision", year=an[y], value = var_prev))
  df_value <- rbind(df_value, data.frame(type = "climato", year=an[y], value = var_clim))
}
### buidling up graph   
  ggplot(df_value, aes(factor(year), value)) + geom_point(aes(fill=type, colour =type))+
  labs(title = paste0(indic[ind], " variance spread"), x="Year", y= "Variance")
  

```
## Ensemble anomaly spread

We compute anomaly for prevision and climatology, following cross validation scheme: considered year is excluded from reference mean.

```{r }
### COMPUTING CROSS VALIDATED ANOMALY  ------------------------------------------------------------------------
df_value <- data.frame()
clim_seasmean <- apply(clim_mean[,,],c(1,2), mean) # seasonal averaging
prev_seasmean <- apply(prev_mean[,,],c(1,2), mean) # seasonal averaging

for (y in 1:nan){
  ref_seasmean <- apply(array_obs[,-y,],c(1), mean) # average over season + years, omitting year y for crossval scheme
  anomaly_ps <- prev_seasmean[,y] - ref_seasmean
  anomaly_clim <- clim_seasmean[,y] - ref_seasmean
  df_value <- rbind(df_value, data.frame(type = "model", year=an[y], value = anomaly_ps))
  df_value <- rbind(df_value, data.frame(type = "climato", year=an[y], value = anomaly_clim))

}
  
  
### YEARLY BOXPLOTS  ------------------------------------------------------------------------
  ggplot(df_value, aes(factor(year), value)) + geom_boxplot(aes(fill=type))+
  labs(title = paste0(indic[ind], " anomaly spread"), x="Year", y= "Indicator value")
  

```
