---
title: "Taylor Diagram"
output: html_document
---

```{r}

dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 

library(plotrix)

```

## Parameters 

```{r }

# variable
ind <- 2

# temporal agregation
temp <- 4:6
ntemp <- length(temp)

# chosen quantile
kantile <- "quint" # ter or quint

# bootstrap and cores
no_core <- 6
nboot <- 100

if (kantile=="quint"){
  proba = 1:4/5; events = 5
} else { proba = 1:2/3; events = 3}

```

## Retrieving original data set

we have to do a trick to find out the first bootstrapped iteration and the run index whithin this iteration matching the year we are interested in (the random sampling doesn't respect chronology)

```{r }

ps_original <- array(NA, dim=c(ngrids, nan, nrun, ntemp))
ref_original <- array(NA, dim=c(ngrids, nan, ntemp))

 for (year in an){
 y <- which(an==year)

       # bootstrap iteration index of the year selected
    load(file = file.path(dir_data, "extract", "years.RData")) # list of years in each bootstrap iteration
     
    list_match <- lapply(rand_year, function(x) which(year == x)) # list of matchs between list of years randomly generated for the bootstrap and the year we are interested in
     
     y_index <- list_match[[1]] # year index within the bootstrap iteration
     b_index <- 1 # bootstrap iteration index
     for (b in 1:(nboot-1)){ # pick the first iteration and first index matching the year we are looking for
       if (length(list_match[[b]])<1 & length(y_index)<1) {y_index <- list_match[[b+1]]; b_index <- b+1}
       else {y_index <- y_index; b_index <- b_index}
     }
     
  nom_prev <- paste0(indic[ind],b_index,"_prev.RData")
  load(file = file.path(dir_data, "extract", nom_prev))
  ps_original[,y,,] <- array_prev[,y_index[1],,temp]
  
  nom_ref <- paste0(indic[ind],b_index,"_ref.RData")
  load(file = file.path(dir_data, "extract", nom_ref))
  ref_original[,y,] <- array_obs[,y_index[1],temp]
}

```
## Data aggregation

We compute temporal and ensemble aggregation: temporal can be a mean or a sum - ensemble mean always

```{r }

ps_agreg <- apply(ps_original[,,,], c(1,2,3), sum)
ps_ensmean <- apply(ps_agreg, c(1,2), mean)
ref_agreg <- apply(ref_original[,,], c(1,2), sum)

```

## Taylor diagram

Scores computed for each grid separately, so they are also plotted separately.

```{r}

taylor.diagram(ref=ref_agreg[1,], model=ps_ensmean[1,],pos.cor=FALSE)
taylor.diagram(ref=ref_agreg[2,], model=ps_ensmean[2,],pos.cor=FALSE, add=TRUE, col= "blue")
taylor.diagram(ref=ref_agreg[3,], model=ps_ensmean[3,],pos.cor=FALSE, add=TRUE, col= "brown")
taylor.diagram(ref=ref_agreg[4,], model=ps_ensmean[4,],pos.cor=FALSE, add=TRUE, col= "red")
taylor.diagram(ref=ref_agreg[5,], model=ps_ensmean[5,],pos.cor=FALSE, add=TRUE, col= "orange")

```
