---
title: "Transforming into probabilistic regarding quintiles"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure"

library(dplyr)
library(stats)
library(foreach)
library(iterators)
library(parallel)
library(doParallel)
library(easyVerification)

no_core <- 6
e <- 5
nboot <- 100
month <- 4:6
```

## Transforming continuous arrays 

Regarding 4 selected events (higher/lower tercile/quintile) reference continuous values are transformed into binary values; ensemble prevision values are transformed into probabilistic values (computed from the ensemble spread). 
we have to do a trick to find out the first bootstrapped iteration and the run index whithin this iteration matching the year we are interested in (the random sampling doesn't respect chronology)


```{r}
tictoc::tic()

for (ind in c(2,3,4,8)){
  
 cl <- makeCluster(no_core)
 registerDoParallel(cl)
 foreach(b=1:nboot, .packages=c("tidyverse","easyVerification")) %dopar%  { # loop on bootstrap samples
    
    nom_ref <- paste0(indic[ind],b,"_ref.RData")
    nom_prev <- paste0(indic[ind],b,"_prev.RData")
    
    load(file = file.path(dir_data, "extract", nom_ref))
    load(file = file.path(dir_data, "extract", nom_prev))
    
    ## SEASONAL ##
    
    int_obs <- apply(array_obs[,,month],c(1,2), sum)
    int_prev <- apply(array_prev[,,,month],c(1,2,3), sum)
    seasbin_ref <- array (NA, dim=c(ngrids,nan,e))
    seasprob_ps <- array (NA, dim=c(ngrids,nan,e))
    for (i in 1:ngrids){
    seasbin_ref[i,,] <- count2prob(convert2prob(int_obs[i,], prob = 1:4/5), type = 4)
    seasprob_ps[i,,] <- count2prob(convert2prob(int_prev[i,,], prob = 1:4/5), type = 4)
    }
    
    nom_prevseas <- paste0(indic[ind],b,"_seasquint_prev.RData")
    nom_refseas <- paste0(indic[ind],b,"_seasquint_obs.RData")
    
    save(seasprob_ps, file = file.path(dir_data, "extract", nom_prevseas))
    save(seasbin_ref, file = file.path(dir_data, "extract", nom_refseas))
    
    ## MONTHLY ##
    
    # if (ind != 3|4|5) { # continuous indicators only
    #   monthbin_ref <- array (NA, dim=c(ngrids,nan,ndimT,e))
    #   monthprob_ps <- array (NA, dim=c(ngrids,nan,ndimT,e))
    # 
    #   for (t in 1:ndimT){
    #     for (i in 1:ngrids){
    #       monthbin_ref[i,,t,] <- count2prob(convert2prob(array_obs[i,,t], prob = 1:4/5), type = 4)
    #       monthprob_ps[i,,t,] <- count2prob(convert2prob(array_prev[i,,,t], prob = 1:4/5), type = 4)
    #     }
    #   }
    # 
    #   nom_prevmonth <- paste0(indic[ind],b,"_monthquint_prev.RData")
    #   nom_refmonth <- paste0(indic[ind],b,"_monthquint_obs.RData")
    #   
    #   save(monthprob_ps, file = file.path(dir_data, "extract", nom_prevmonth))
    #   save(monthbin_ref, file = file.path(dir_data, "extract", nom_refmonth))
    # }
    
  }
  
  stopCluster(cl)
  
}

tictoc::toc()

```
