---
title: "visu_data"
output: html_document
---

```{r setup, include=FALSE}
dir_data <- "D:/HOME/ekamir/scoring_medscope/data/season_trial2" 
dir_plot <- "D:/HOME/ekamir/scoring_medscope/figure" 
library(maps)
library(maptools)
library(rasterVis)
library(ggplot2)
library(latticeExtra)
library(sp)
library(raster)
library(rgdal)
library(tmap)
library(sf)

```


## Loading files

Extracted selected indicator values and grid coordinates loaded.

```{r file loading}
# parameter specification
ind <- 2 # indicator

# file loading
nom_ref <- paste0(indic[ind],"_ref.RData")
nom_prev <- paste0(indic[ind],"_prev.RData")
nom_clim <- paste0(indic[ind],"_clim.RData")
nom_av_clim <- paste0(indic[ind],"_ensmean_clim.RData")
nom_av_prev <- paste0(indic[ind],"_ensmean_prev.RData")

load(file = file.path(dir_data, "extract", nom_ref))
load(file = file.path(dir_data, "extract", nom_prev))
load(file = file.path(dir_data, "extract", nom_clim))
load(file = file.path(dir_data, "extract", nom_av_clim))
load(file = file.path(dir_data, "extract", nom_av_prev))

load(file = file.path(dir_data, "extract", "lon.RData"))
load(file = file.path(dir_data, "extract", "lat.RData"))

```

## Transforming data frames into raster

We pick a year and compute the seasonal ensemble mean. then we transform dataframes into rasters using coordinates previously loaded. 

```{r }

# parameter specification
year <- 2

# averaging over t dimension
clim_values <- apply(clim_mean[,year,],c(1), mean)
prev_values <- apply(prev_mean[,year,],c(1), mean)
obs_values <- apply(array_obs[,year,],c(1), mean)

# creating shapefiles of values to be plotted
df_prev <- data.frame(longitude=vect_lon, latitude=vect_lat, indicator=prev_values)
df_clim <- data.frame(longitude=vect_lon, latitude=vect_lat, indicator=clim_values)
df_obs <- data.frame(longitude=vect_lon, latitude=vect_lat, indicator=obs_values)

coordinates(df_prev) <- ~lon+lat ### ISSUES COLUMN NAMING !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
coordinates(df_clim) <- ~lon+lat
coordinates(df_obs) <- ~lon+lat

proj4string(df_prev) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
proj4string(df_clim) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")
proj4string(df_obs) <- CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")

sp_prev <- st_as_sf(df_prev)
sp_clim <- st_as_sf(df_clim)
sp_obs <- st_as_sf(df_obs)

plot(sp_prev, nbreaks = 40)
plot(sp_clim, nbreaks = 40)
plot(sp_obs, nbreaks = 40)

# transform shp into raster to get data extent 
ras_prev <- raster(sp_prev)
ras_clim <- raster(sp_clim)
ras_obs <- raster(sp_obs)

ext_prev <- extent(ras_prev)
ext_clim <- extent(ras_clim)
ext_obs <- extent(ras_obs)

# create background raster 
mask.raster <- raster(resolution=c(0.1,0.07), crs = "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0", ## !!!!!!!!!!!
                      ext = ext_prev)

# convert the shapefile to a raster based on background raster
ras_prev_complete <- rasterize(sp_prev, mask.raster)
ras_clim_complete <- rasterize(sp_clim, mask.raster)
ras_obs_complete <- rasterize(sp_obs, mask.raster)

plot(ras_prev_complete$indicator)

```
### Mapping indicator values

Now that we have transformed the data frame into a raster we will map them using 'tmap' package, and save the maps all together using 'tmap_arrange' function.

```{r }
titre_prev <- paste0("Prevision ensemble seasonal mean ", an[year])
titre_clim <- paste0("Climato ensemble seasonal mean ", an[year])
titre_obs <- paste0("Reference seasonal mean ", an[year])

data("World")
ramp = colorRampPalette(c("lightblue", "red"))
relief_shp <- st_read(dsn=file.path(dir_data, "communes-20190101.shp")) #  to be replaces by rivers etc...?????
riviere_shp <- st_read(dsn=file.path(dir_data, "relief_naturel.shp")) #  to be replaces by rivers etc...?????

prev_map <- tm_shape(ras_prev_complete$tercile)+
  tm_raster( title = titre_prev, palette = '-RdBu',
             legend.reverse = TRUE)+
  tm_legend(outside=TRUE, hist.width=2)+
  tm_layout(legend.position = c("left", "bottom"))

clim_map <- tm_shape(ras_clim_complete$indicator)+
  tm_raster( title = titre_clim, palette = '-RdBu',
             legend.reverse = TRUE)+
  tm_legend(outside=TRUE, hist.width=2)+
  tm_layout(legend.position = c("left", "bottom"))

obs_map <- tm_shape(ras_obs_complete$indicator)+
  tm_raster( title = titre_obs, palette = '-RdBu',
             legend.reverse = TRUE)+
  tm_legend(outside=TRUE, hist.width=2)+
  tm_layout(legend.position = c("left", "bottom"))

### SAVING MAP    -------------------------------------------------------------------------------------
tiff(paste0(an[year], " seasonal_ens_mean.tiff"), width = 8, height = 5, units = 'in', res = 300, compression = 'none')
tmap_arrange(prev_map, clim_map, obs_map, asp = 1)
dev.off()

```






